Paper One Summary

### 2015-09-03 hw/read/1/summary.tex
Merged motivational statement, expanded on results, fixed typos

\section*{Feature Extraction}
\begin{itemize}
\item \textbf{Motivational Statements} Modern software applications are
composed of many files. Thus, the files are usually organized into
units, which may themselves be organized into broader units. While
research could be focused at the most granular level, for example
files, methods, even lines of code, research at these levels is costly
and takes time, so research instead usually examines data at higher
levels. Therefore, it would be useful to draw conclusions from higher
levels that would apply to lower levels. 
\item \textbf{Related Work} To improve model performance, Koru \textit{et
al.} recommend aggregating. Their methods to acheive improved performance
include summing method-level measures into class-level measures and
combining these with metrics from class-level features. They conclude
that this approach overcomes the issues of asymmetry in defect data
sets. Schröter \textit{et al.} conclude that predicting at coarser
granularities is less difficult in comparison to finer granularities
but lead to worse results. Zimmerman \textit{et al.} find different
results where package level correlations and model correlations are
higher than file level correlations and model correlations. Ambrose
\textit{et al.} argue against the use of aggregate level metrics,
though without data, stating predictions are more cumbersome to investigate,classes
are inherently self-contained, and information derived from the package-level
cannot be applied to the class level. 
\item \textbf{Motivational Statements}: The authors poses their motivation
along with the central question of the paper \textquotedbl{}What is
the right level of study?\textquotedbl{} (At an aggregated level or
dis-aggregated level). They believe that this question has a central
significance to whether or not a model that is built at a specific
level of aggregation can hold at a lower level of aggregation as well
as whether performance of the model as regards cost prediction is
valid. 
\item \textbf{New Results}: The authors grouped variables in the models
based on loss of significance(LS) or gain of significance(GS). They
explain that both LS and GS can cause Ecological Inferences issues
as in a loss of significance situation when inferring between the
aggregate level and the disaggregate level or GS when inferring from
the disaggregate to the aggregate. They found 28 instances of GS and
25 instances of LS out of 108 variables over 68 models. The authors
draw the conclusion that models built at the aggregated level should
be undertaken with the knowledge of the underlying risk of Ecological
Inference and Ecological Fallacy. 
\item \textbf{Future Work}:The authors bring up three sources of Ecological
Inference risk: Zonation, Sample Size, and Class Imbalance. The authors
believe that further study of the three sources is in order. To give
a short background on how each applies:

@@

\section*{Possible Improvements}
\begin{itemize}
\item There are some particularly distracting typos in the paper. For example,
on pages 367-368 the authors failed to correctly reference their table
correctly leaving \textquotedbl{}Table ??\textquotedbl{} in the middle
of their text twice. 
\item The authors could have provided a better explanation of AUCROC and
AUCCE and the meaning of their results with respect to those measures.
The authors did a good job of comparing file and package measures,
but did not explain why file AUCCE was lower than file AUCROC. Is
this just the nature of AUCCE since it is including cost effectiveness?
Why was there more variance in the AUCCE measures than AUCROC?
\item At the end of the paper, the authors provide a brief note about threats
to the external validity of the results. The authors only examined
projects from one source: the Apache Software Foundation. Analyzing
projects from other sources which employ different software engineering
principles or which organize their projects differently would bolster
their results and conclusions.\end{itemize}

>>>>

\section*{Feature Extraction}
\begin{itemize}
\item \textbf{Motivational Statements} Modern software applications are
composed of many files. Thus, the files are usually organized into
units, which may themselves be organized into broader units. While
research could be focused at the most granular level, for example
files, methods, even lines of code, modeling at these levels is costly
and takes time. The authors motivation is determine if statistical models built at an aggregated level are valid at the dis-aggregated level. A second motivation is to asses the cost-effectiveness of predication models at varying aggregated levels.
\item \textbf{Related Work} To improve model performance, Koru \textit{et
al.} recommend aggregating. Their methods to acheive improved performance
include summing method-level measures into class-level measures and
combining these with metrics from class-level features. They conclude
that this approach overcomes the issues of asymmetry in defect data
sets. Schröter \textit{et al.} conclude that predicting at coarser
granularities is less difficult in comparison to finer granularities
but lead to worse results. Zimmerman \textit{et al.} find different
results where package level correlations and model correlations are
higher than file level correlations and model correlations. Ambrose
\textit{et al.} argue against the use of aggregate level metrics,
though without data, stating predictions are more cumbersome to investigate,classes
are inherently self-contained, and information derived from the package-level
cannot be applied to the class level. 
\item \textbf{New Results}: The authors grouped features in the models
based on loss of significance(LS) or gain of significance(GS). Both of these can result in Ecological Fallacy. 
LS is a loss of significance when inferring from the
aggregate level to the disaggregate level. GS is a gain of significance from the aggregate level to the file level. They found 28 instances of GS and
25 instances of LS out of 108 features over 68 models. The authors
draw the conclusion that models built at the aggregated level should
be undertaken with the knowledge of the underlying risk of Ecological
Inference and Ecological Fallacy. The author's also provided data showing the advantages of AUCCE over AUCROC when comparing models at different levels of aggregation. These results lead to two final conclusions: aggregated prediction models can evaluate better than actual when applied to aggregated data and as a consequence models build at an aggregated level may not be applicable to the dis-aggregated level.
\item \textbf{Future Work}:The authors bring up three sources of Ecological
Inference risk: Zonation, Sample Size, and Class Imbalance. The authors
believe that further study of the three sources is in order. To give
a short background on how each applies:

@@

\section*{Possible Improvements}
\begin{itemize}
\item There are some particularly distracting typos in the paper. For example,
on pages 367-368 the authors failed to correctly reference their table
correctly leaving \textquotedbl{}Table ??\textquotedbl{} in the middle
of their text twice. 
\item The authors could have provided a better explanation of AUCROC and
AUCCE and the meaning of their results with respect to those measures.
The authors did a good job of comparing file and package measures,
but did not explain why file AUCCE was lower than file AUCROC. Is
this just the nature of AUCCE since it is including cost effectiveness?
Why was there more variance in the AUCCE measures than AUCROC?
\item At the end of the paper, the authors provide a brief note about threats
to the external validity of the results. The authors only examined
projects from one source: the Apache Software Foundation. Analyzing
projects from other sources which employ different software engineering
principles or which organize their projects differently would bolster
their results and conclusions.
\end{itemize}
